Properties of coronal Fourier power spectra and their implications for coronal seismology and solar atmospheric heating.

### 2014-05-06 tex/paper1/paper1.tex
testing the analysis

\title{Properties of coronal Fourier power spectra and their
  implications for coronal seismology and coronal heating.}

@@

\begin{abstract}
The Fourier power spectra of regions of the solar corona are
investigated using AIA 171\AA\ and 193\AA\ data.  It is shown that the
Fourier power spectra in all the regions show a power law behaviour
approximately.  This suggests that in many parts of the corona a
background model consisting of white noise and a trend cannot be
assumed when analyzing for the presence of oscillations in the corona.
Further, it is shown that the observed power law power spectrum is
consistent with that expected from summing a distribution of
exponentially decaying emission events along the line of sight.  This
is consistent with the notion that the corona is heated everywhere by
small energy deposition events, such as nanoflares.
\end{abstract}

@@

There has been a considerable amount of work in modeling the
AIA-detected plasma response.  \cite{}

>>>>

\title{Properties of coronal Fourier power spectra and their
  implications for coronal seismology and solar atmospheric heating.}

@@

\begin{abstract}
The Fourier power spectra of regions of the solar corona are
investigated using AIA 171\AA\ and 193\AA\ data.  It is shown that the
Fourier power spectra in all the regions show a power law behaviour
approximately.  This suggests that in many parts of the corona a
background model consisting of white noise and a trend cannot be
assumed when analyzing for the presence of oscillations in the corona.
Further, it is shown that the observed power law power spectrum can be
formed by summing a distribution of exponentially decaying emission
events along the line of sight.  This is consistent with the notion
that the solar atmosphere is heated everywhere by small energy
deposition events.
\end{abstract}

@@

There has been a considerable amount of work in modeling the
AIA-detected plasma response...  \cite{}
